---
author: "Fernando Moreno Jabato"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<style type='text/css'>
    body .main-container {
        max-width: 90%;
    }

    .plot_real_size {
    	overflow: scroll;
  	}

    .plot_real_size img{
    	max-width: none;
    	max-height: none;
    }

    embed {
   		width: 800px;
  		height: 800px;
  }   
</style>

```{r config, include = FALSE}
 
# Load necessary packages
require(ggplot2)
require(knitr)

# Prepare recursive text
chunks <- function(code, options = ""){paste(paste("```{r ",options,"}",sep = ""),code,"```",sep="\n")}
render <- function(text){paste(knit(text = paste(text,collapse = "\n")),collapse = "\n")}

# Prepare all HPO reports container
out <- NULL
n_category <- 30

```




# **DEgenes Hunter - CLUSTER `r cl` - Functional analysis report** 


## **Used data in this analysis**
Specifically, in this experiment set, known experiment labels are:

```{r add_exp_names, echo = FALSE}
	# Obtain experiments names
	# dir <- dirname(opt$countdata_file)
	# experiments <- read.table(file = file.path(dir,"control_treatment.txt"), sep = "\t", quote = "", header = TRUE, stringsAsFactors = FALSE)
	# exp_names <- experiments[which(experiments[,1] == "T"),2]

	out <- unlist(lapply(exp_names,function(names){paste("* ",names,sep="")}))
```

`r paste(knit(text = paste(out,collapse = "\n")),collapse = "\n")`


## **General description**
This report contains all the functional information that was requested by the options when functional_Hunter.R was executed.
The functional categories can be:

* KEGG pathways
* GO:
	+ Biological Process
	+ Molecular Function
	+ Cellular Component
* Reactome pathways
* Custom nomenclature

All the functional categories are computed with CluterProfiler and GO caterogires are computed also with TopGo.
Some sections will not show if there are not sinficative results. Each category is analysed using Over representation analysis (ORA) and Gene Set Analysis (GSEA).
The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.
In the case of the GSEA method, all the genes are sorted by their fold-change and the algorithm scan which genes with similar fold-change shares a term of the selected functional category.


Statistics about input results obtained from DEGenes Expression Hunter are:
```{r table_exp_flags, echo = FALSE}
cl_table <- as.data.frame(table(DEG_annot_table$genes_tag[which(DEG_annot_table$Cluster_ID == cl)]))
names(cl_table) <- c("Gene_tag","Genes")
knitr::kable(cl_table)
```

```{r load_correlation_stats, echo = FALSE}
curr_out <- knit_expand("partial/corr_cl_stats.Rmd")
```

`r paste(knit(text = curr_out), collapse = '\n')`

```{r load_ORA_results, echo = FALSE, eval = exists("enrichments_ORA_expanded")}
# Per each category defined, perform enrichment
curr_out <- unlist(lapply(names(enrichments_ORA_expanded),function(cat){
  sec_text <- paste(c("## **",cat," enrichment results**\n"),collapse="") # Header
  sec_text <- c(sec_text,knit_expand("partial/ora_enrichResult.Rmd")) # Body
  return(sec_text)
}))
```
`r paste(knit(text = curr_out), collapse = '\n')`


```{r load_ORA_customResults, echo = FALSE}
curr_out <- ""

if(exists("custom_cls_ORA")){
  # Per each custom category defined, perform enrichment
  curr_out <- unlist(lapply(names(custom_cls_ORA),function(cat){
    sec_text <- paste(c("## **",basename(cat)," custom enrichment results**\n"),collapse="") # Header
    sec_text <- c(sec_text,knit_expand("partial/ora_customEnrichResult.Rmd")) # Body
    return(sec_text)
  }))
}
```
`r paste(knit(text = curr_out), collapse = '\n')`

