---
author: "Fernando Moreno Jabato"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
    	overflow: scroll;
  		max-height: 600px;
  	}

    .plot_real_size img{
    	max-width: none;
    	max-height: none;
    }

    embed {
   
  }   
</style>

```{r config, include = FALSE}
n_category <- 30
base_width <- 30


# Load necessary packages
require(ggplot2)
require(knitr)
require(plyr)
require(clusterProfiler)

# Prepare recursive text
chunks <- function(code, options = ""){paste(paste("```{r ",options,"}",sep = ""),code,"```",sep="\n")}
render <- function(text){paste(knit(text = paste(text,collapse = "\n")),collapse = "\n")}

# Prepare all HPO reports container
out <- NULL

# Check executed modules
all_posible <- c("GO_BP","GO_CC","GO_MF","KEGG","REACT")
if(exists("enrichments_ORA")){ executed <- as.list(all_posible %in% names(enrichments_ORA))
}else{ executed <- as.list(all_posible %in% names(enrichments_GSEA))}
names(executed) <- all_posible

# Prepare resize function
#################################################################################
############### Resizing plot functions
###############################################################################
resize <- function(g, fig_height=5, fig_width=12) {
  g_deparsed <- paste0(deparse(function() {g}), collapse = '')
  sub_chunk <- paste0("\n```{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=", fig_height, ", fig.width=", fig_width, ", echo=FALSE}", "\n(", g_deparsed, ")()\n```\n\n\n")
  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}

plot_in_div <- function(plot, height = 7, width = 12) {

  cat('\n<div class="plot_real_size">\n')
  resize(plot, height, width)
  cat('\n</div>\n')
}

get_plot_df <- function(enrich_obj, showCategory = 30) {
  geneSets <- enrichplot:::extract_geneSets(enrich_obj, enrichplot:::update_n(enrich_obj, showCategory))
  geneSets <- enrichplot:::list2df(geneSets)
  return(geneSets)
}

get_categories <- function(enrich_obj, showCategory = n_category){
	enrich_obj_class <- class(enrich_obj)[1]
	if(enrich_obj_class == "enrichResult"){
    	categories <- get_plot_df(enrich_obj, showCategory)$categoryID
  	}else if(enrich_obj_class == "compareClusterResult"){
    	categories <- enrich_obj@compareClusterResult$Description
  	}else{
    	warning("Not valid enrich object")
  	}
  	return(unique(categories))
}


get_clusters <- function(compareCluster_obj){
    all_clusters <- enrichments_ORA$REACT@compareClusterResult$Cluster
    return(unique(all_clusters))
}

get_genes <- function(enrich_obj, showCategory = 30){
  genes <- get_plot_df(enrich_obj, showCategory)$Gene
  return(unique(genes))
}

calc_width <- function(enrich_obj, showCategory = 30, category_character_size = 0.035, character_width = 3, legend_size = 1){
	enrich_obj_class <- class(enrich_obj)[1]
	if(enrich_obj_class == "enrichResult"){
		longer_x_element <- length(get_genes(enrich_obj, showCategory))
	}else if(enrich_obj_class == "compareClusterResult"){
    	longer_x_element <- length(get_clusters(enrich_obj))
  	}else{
    	warning("Not valid enrich object")
	}

	width_size <- (legend_size + (category_character_size * max(nchar(as.character(get_categories(enrich_obj, showCategory))))) + (character_width * longer_x_element))
	cat(paste0("Real width is ", width_size, " inches"))

  	if(width_size > 100){
		width_size <- 50
	}
 	return(width_size)

}

calc_height <- function(enrich_obj, showCategory = NA, min_size = 7, gene_character_size = 3, category_name_size = 0.1){
	enrich_obj_class <- class(enrich_obj)[1]
	if(enrich_obj_class == "enrichResult"){
		plot_area_elements <- max(nchar(as.character(get_genes(enrich_obj, showCategory = showCategory))))
	}else if(enrich_obj_class == "compareClusterResult"){
    	plot_area_elements <- 2
  	}else{
    	warning("Not valid enrich object")
	}
	if(!is.na(showCategory)){
		categories <- showCategory
	} else {
		categories <- length(get_categories(enrich_obj))

	}
  	height_size <- (gene_character_size* plot_area_elements) + (category_name_size * categories)
  #	height_size <- height_size * 0.5
  	# cat(paste0("Real height is ", height_size, " inches"))
	if(height_size < min_size){
		height_size <- min_size
	} else if(height_size > 100){
		height_size <- 50
	}
  	# message(paste0("Used width of ", height_size, " inches"))

  return(height_size)
}

set_default_width <- function(enrich_obj, default = 12, showCategory = 30, threshold = 30, character_size = 0.04){
	longer_category <- max(nchar(as.character(get_categories(enrich_obj, showCategory))))
	if(longer_category > threshold){
		default_width <- default + character_size * longer_category
	}else{
		default_width <- default
	}
	return(default_width)
}
clusters_heatplot <- function(compare_cluster_obj){
	pp <- ggplot(compare_cluster_obj, aes(x = Cluster, y = Description, fill = p.adjust)) + 
	geom_tile()	
}
set_standard_size <- function(pp){
	pp <- pp + theme_light() + 
        theme(axis.text.y = element_text(size = 10, face = 'bold'), axis.title = element_blank()) 
	return(pp)
}
#############################################################################
############### END
#############################################################################
```




# **DEgenes Hunter - Clusters functional analysis main report** 


## **Used data in this analysis**
Specifically, in this experiment set, known experiment labels are:

```{r add_exp_names, echo = FALSE}
	out <- unlist(lapply(exp_names,function(names){paste("* ",names,sep="")}))
```

`r paste(knit(text = paste(out,collapse = "\n")),collapse = "\n")`


## **General description**
This report contains all the functional information that was requested by the options when functional_Hunter.R was executed using a **clusterized set**.
The functional categories can be:

* KEGG pathways
* GO:
	+ Biological Process
	+ Molecular Function
	+ Cellular Component
* Reactome pathways
* Custom nomenclature

All the functional categories are computed with CluterProfiler and GO caterogires are computed also with TopGo.
Some sections will not show if there are not sinficative results. Each category is analysed using Over representation analysis (ORA) and Gene Set Analysis (GSEA).
The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.
In the case of the GSEA method, all the genes are sorted by their fold-change and the algorithm scan which genes with similar fold-change shares a term of the selected functional category.

Clusters defined (rows) into input data and their genes amount labeled with expression analysis (columns) and enriched terms of each module (columns at the end) are:
```{r cls_table, echo = FALSE}
# Obtains genes info
cls_counts <- ddply(DEG_annot_table, .(DEG_annot_table$genes_tag,DEG_annot_table$Cluster_ID), nrow)
names(cls_counts) <- c("Gene_Tag","Cluster_ID","Freq")
# Prepare columns
aux <- unique(cls_counts$Gene_Tag)
if(exists("enrichments_ORA")) aux <- c(aux,paste(names(executed)[which(unlist(executed))],"(ORA)"))
if(exists("enrichments_GSEA")) aux <- c(aux,paste(names(executed)[which(unlist(executed))],"(GSEA)"))
# Prepare freqs
cls_genes_summary <- matrix(0,nrow = length(unique(cls_counts$Cluster_ID)),ncol = length(aux))
rownames(cls_genes_summary) <- unique(cls_counts$Cluster_ID)
colnames(cls_genes_summary) <- aux
invisible(lapply(seq(nrow(cls_counts)),function(i){cls_genes_summary[which(rownames(cls_genes_summary) == cls_counts$Cluster_ID[i]),which(colnames(cls_genes_summary) == cls_counts$Gene_Tag[i])] <<- cls_counts$Freq[i]}))
# Obtain info for executed modules
invisible(lapply(names(executed)[which(unlist(executed))],function(mod){
	invisible(lapply(rownames(cls_genes_summary),function(cl){
		message(cl)
		if(exists("enrichments_ORA")) cls_genes_summary[cl,paste(mod,"(ORA)")] <<- length(which(enrichments_ORA[[mod]]@compareClusterResult$Cluster == cl))
		if(exists("enrichments_GSEA")) cls_genes_summary[cl,paste(mod,"(GSEA)")] <<- length(which(enrichments_GSEA[[mod]]@compareClusterResult$Cluster == cl))
	}))
}))
# Render
knitr::kable(cls_genes_summary)
```

And executed modules have been:
```{r executed_modules, echo = FALSE}
knitr::kable(data.frame(Executed = unlist(executed)))
```

```{r kegg_main,  results='asis', echo = FALSE, eval = executed[["KEGG"]]}
cat("## **KEGG analysis**\n")
```
```{r kegg_ora, results='asis', echo=FALSE, eval = executed[["KEGG"]] & exists("enrichments_ORA"), message = FALSE}

cat("### **Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
message("Printing dotplot")
cat(length(get_categories(enrichments_ORA$KEGG)))
pp <- dotplot(enrichments_ORA$KEGG, showCategory=n_category) 
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$KEGG),calc_width(enrichments_ORA$KEGG))




cat(
	"**Heatmap**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
message("Printing heatplot")

pp <- clusters_heatplot(enrichments_ORA$KEGG@compareClusterResult)  
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$KEGG),calc_width(enrichments_ORA$KEGG))


cat(
	"**CNetplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
message("Printing cnetplot")

pp <- cnetplot(enrichments_ORA$KEGG, showCategory = n_category)
plot_in_div(pp, calc_height(enrichments_ORA$KEGG), calc_width(enrichments_ORA$KEGG))
message("Ploting ended")


```



```{r reac_main,  results='asis', echo = FALSE, eval = executed[["REACT"]]}
cat("## **Reactome analysis**\n")
```
```{r reac_ora, results='asis', echo=FALSE, eval = executed[["REACT"]] & exists("enrichments_ORA")}

cat("### **Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
cat(length(get_categories(enrichments_ORA$REACT)))

pp <- dotplot(enrichments_ORA$REACT, showCategory=n_category)  
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$REACT),calc_width(enrichments_ORA$REACT))


cat(
	"**Heatmap**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- clusters_heatplot(enrichments_ORA$REACT@compareClusterResult)  
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$REACT),calc_width(enrichments_ORA$REACT))


cat(
	"**CNetplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- cnetplot(enrichments_ORA$REACT, showCategory = n_category)
plot_in_div(pp, calc_height(enrichments_ORA$REACT),calc_width(enrichments_ORA$REACT))

```




```{r go_main,  results='asis', echo = FALSE, eval = any(executed[["GO_BP"]],executed[["GO_MF"]],executed[["GO_CC"]])}
cat("## **Gene Ontology (GO) analysis**\n")
```

```{r go_bp_ora, results='asis', echo=FALSE, eval = all(executed[["GO_BP"]],exists("enrichments_ORA"))}

cat("### **[BP] Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
cat(length(unique(get_categories(enrichments_ORA$GO_BP, showCategory = n_category))))

pp <- dotplot(enrichments_ORA$GO_BP, showCategory=n_category)  
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$GO_BP, showCategory=n_category),calc_width(enrichments_ORA$GO_BP))


cat(
	"**Heatmap**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- clusters_heatplot(enrichments_ORA$REACT@compareClusterResult) 
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$GO_BP),calc_width(enrichments_ORA$GO_BP))


cat(
	"**CNetplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- cnetplot(enrichments_ORA$GO_BP, showCategory = n_category)
plot_in_div(pp, calc_height(enrichments_ORA$GO_BP),calc_width(enrichments_ORA$GO_BP))


```

```{r go_mf_ora, results='asis', echo=FALSE, eval = all(executed[["GO_MF"]],exists("enrichments_ORA"))}

cat("### **[MF] Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
pp <- dotplot(enrichments_ORA$GO_MF, showCategory=n_category)  
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$GO_MF),calc_width(enrichments_ORA$GO_MF))

cat(
	"**Heatmap**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- clusters_heatplot(enrichments_ORA$GO_MF@compareClusterResult) 
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$GO_MF),calc_width(enrichments_ORA$GO_MF))

cat(
	"**CNetplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)
pp <- cnetplot(enrichments_ORA$GO_MF, showCategory = n_category)
plot_in_div(pp, calc_height(enrichments_ORA$GO_MF),calc_width(enrichments_ORA$GO_MF))

```

```{r go_cc_ora, results='asis', echo=FALSE, eval = all(executed[["GO_CC"]],exists("enrichments_ORA"))}

cat("### **[CC] Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- dotplot(enrichments_ORA$GO_CC, showCategory=n_category)  
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$GO_CC),calc_width(enrichments_ORA$GO_CC))


cat(
	"**Heatmap**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- clusters_heatplot(enrichments_ORA$GO_CC@compareClusterResult) 
pp <- set_standard_size(pp)
plot_in_div(pp, calc_height(enrichments_ORA$GO_CC),calc_width(enrichments_ORA$GO_CC))

cat(
	"**CNetplot**\n\n", 
	"WRITE THIS TEXT >>>>.\n\n"
)

pp <- cnetplot(enrichments_ORA$GO_CC, showCategory = n_category)
plot_in_div(pp, calc_height(enrichments_ORA$GO_CC),calc_width(enrichments_ORA$GO_CC))

```




```{r create_out_custom, echo = FALSE}
out_custom <- ""
```

```{r custom_create, echo = FALSE, eval = exists("custom_cls_ORA")}
out_custom <- NULL
invisible(lapply(seq_along(custom_cls_ORA),function(i){
	# Take results
	res <- custom_cls_ORA[[i]]
	cname <- names(custom_cls_ORA)[i]
	# Check and generate info
	if(is.null(res)){
		header <- "## **{{cname}}** \n\nThis CUSTOM study has been executed but **has not returned any result**\n"
		body <- ""
	}else{
		header <- ""

		body <- "res <- custom_cls_ORA[[{{i}}]]
				cname <- names(custom_cls_ORA)[{{i}}]
				cat('### **{{cname}} -  Over Representation Analysis**\n',
				'The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n')
				cat(
					'**Dotplot**\n\n', 
					'WRITE THIS TEXT >>>>.\n\n'
				)
				pp <- dotplot(res, showCategory=n_category)   
				pp <- set_standard_size(pp)
				plot_in_div( pp, calc_height(res),calc_width(res))

				cat(
					'**Heatmap**\n\n', 
					'WRITE THIS TEXT >>>>.\n\n'
				)

				pp <- clusters_heatplot(res@compareClusterResult) 
				pp <- set_standard_size(pp)
				plot_in_div(pp, calc_height(res),calc_width(res))
				cat(
					'**CNetplot**\n\n', 
					'WRITE THIS TEXT >>>>.\n\n'
				)

				pp <- cnetplot(res, showCategory = n_category)
				plot_in_div(pp, calc_height(res), calc_width(res))

		"

	}
	out_custom <<- c(out_custom,paste(knit_expand(text = paste(header,
										 					chunks(body, options = "echo = FALSE,results='asis'"),
										 					"\n",sep = "\n")),
													sep = "\n"))
}))

```

`r paste(knit(text = paste(out_custom,collapse = "\n")),collapse = "\n")`