---
author: "Fernando Moreno Jabato"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<style type='text/css'>
    body .main-container {
        max-width: 90%;
    }

    .plot_real_size {
    	overflow: scroll;
  	}

    .plot_real_size img{
    	max-width: none;
    	max-height: none;
    }

    embed {
   		width: 800px;
  		height: 800px;
  }   
</style>

```{r config, include = FALSE}
n_category <- 30
base_width <- 30


# Load necessary packages
require(ggplot2)
require(knitr)
require(plyr)
require(clusterProfiler)

# Prepare recursive text
chunks <- function(code, options = ""){paste(paste("```{r ",options,"}",sep = ""),code,"```",sep="\n")}
render <- function(text){paste(knit(text = paste(text,collapse = "\n")),collapse = "\n")}

# Prepare all HPO reports container
out <- NULL

# Prepare resize function
#################################################################################
############### Resizing plot functions
###############################################################################
resize <- function(g, fig_height=5, fig_width=12) {
  g_deparsed <- paste0(deparse(function() {g}), collapse = '')
  sub_chunk <- paste0("\n```{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=", fig_height, ", fig.width=", fig_width, ", echo=FALSE}", "\n(", g_deparsed, ")()\n```\n\n\n")
  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}

plot_in_div <- function(plot, height = 7, width = 12) {
  cat('\n<div class="plot_real_size">\n')
  resize(plot, height, width)
  cat('\n</div>\n')
}

get_plot_df <- function(enrich_obj, showCategory = 30) {
  geneSets <- enrichplot:::extract_geneSets(enrich_obj, enrichplot:::update_n(enrich_obj, showCategory))
  geneSets <- enrichplot:::list2df(geneSets)
  return(geneSets)
}
get_categories <- function(enrich_obj, showCategory = 30){
  categories <- get_plot_df(enrich_obj, showCategory)$categoryID
  return(unique(categories))
}
get_genes <- function(enrich_obj, showCategory = 30){
  genes <- get_plot_df(enrich_obj, showCategory)$Gene
  return(unique(genes))
}

calc_width <- function(enrich_obj, showCategory = 30, category_character_size = 0.08, genename_size = 0.12, legend_size = 1){
  width_size <- (legend_size + (category_character_size * max(nchar(as.character(get_categories(enrich_obj, showCategory))))) + (genename_size * length(get_genes(enrich_obj, showCategory))))
  return(width_size)
}
calc_height <- function(enrich_obj, showCategory = 30, min_size = 0.3, gene_character_size = 0.08, category_name_size = 0.15){
  height_size <- (min_size +(gene_character_size* max(nchar(as.character(get_genes(enrich_obj, showCategory))))) + (category_name_size * length(get_categories(enrich_obj, showCategory))))
  return(height_size)
}

set_default_width <- function(enrich_obj, default = 12, showCategory = 30, threshold = 30, character_size = 0.04){
	longer_category <- max(nchar(as.character(get_categories(enrich_obj, showCategory))))
	if(longer_category > threshold){
		default_width <- default + character_size * longer_category
	}else{
		default_width <- default
	}
	return(default_width)
}
#############################################################################
############### END
#############################################################################
```




# **DEgenes Hunter - Clusters functional analysis main report** 


## **Used data in this analysis**
Specifically, in this experiment set, known experiment labels are:

```{r add_exp_names, echo = FALSE}
	out <- unlist(lapply(exp_names,function(names){paste("* ",names,sep="")}))
```

`r paste(knit(text = paste(out,collapse = "\n")),collapse = "\n")`


## **General description**
This report contains all the functional information that was requested by the options when functional_Hunter.R was executed using a **clusterized set**.
The functional categories can be:

* KEGG pathways
* GO:
	+ Biological Process
	+ Molecular Function
	+ Cellular Component
* Reactome pathways
* Custom nomenclature

All the functional categories are computed with CluterProfiler and GO caterogires are computed also with TopGo.
Some sections will not show if there are not sinficative results. Each category is analysed using Over representation analysis (ORA) and Gene Set Analysis (GSEA).
The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.
In the case of the GSEA method, all the genes are sorted by their fold-change and the algorithm scan which genes with similar fold-change shares a term of the selected functional category.

Clusters defined (rows) into input data and their genes amount labeled with expression analysis (columns) are:
```{r cls_table, echo = FALSE}
cls_counts <- ddply(DEG_annot_table, .(DEG_annot_table$genes_tag,DEG_annot_table$Cluster_ID), nrow)
names(cls_counts) <- c("Gene_Tag","Cluster_ID","Freq")
cls_genes_summary <- matrix(0,nrow = length(unique(cls_counts$Cluster_ID)),ncol = length(unique(cls_counts$Gene_Tag)))
rownames(cls_genes_summary) <- unique(cls_counts$Cluster_ID)
colnames(cls_genes_summary) <- unique(cls_counts$Gene_Tag)
invisible(lapply(seq(nrow(cls_counts)),function(i){cls_genes_summary[which(rownames(cls_genes_summary) == cls_counts$Cluster_ID[i]),which(colnames(cls_genes_summary) == cls_counts$Gene_Tag[i])] <<- cls_counts$Freq[i]}))
knitr::kable(cls_genes_summary)
```

And executed modules have been:
```{r executed_modules, echo = FALSE}
all_posible <- c("GO_BP","GO_CC","GO_MF","KEGG","REACT")
if(exists("enrichments_ORA")){ executed <- as.list(all_posible %in% names(enrichments_ORA))
}else{ executed <- as.list(all_posible %in% names(enrichments_GSEA))}
names(executed) <- all_posible
knitr::kable(data.frame(Executed = unlist(executed)))
```

```{r kegg_main,  results='asis', echo = FALSE, eval = executed[["KEGG"]]}
cat("## **KEGG analysis**\n")
```
```{r kegg_ora, results='asis', echo=FALSE, eval = executed[["KEGG"]] & exists("enrichments_ORA")}

cat("### **Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"The plot shows the top functional terms in descendant order by gene ratio. This ratio is the proportion of the known genes for a given functional term that are identified in the expression data. The color represents the associated adjusted pvalue. 
	The X axis represents the gene ratio and the dot size the number of DEG genes associated to the functional term.\n\n"
)
pp <- dotplot(enrichments_ORA$KEGG, showCategory=n_category)
plot(pp)
```



```{r reac_main,  results='asis', echo = FALSE, eval = executed[["REACT"]]}
cat("## **Reactome analysis**\n")
```
```{r reac_ora, results='asis', echo=FALSE, eval = executed[["REACT"]] & exists("enrichments_ORA")}

cat("### **Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"The plot shows the top functional terms in descendant order by gene ratio. This ratio is the proportion of the known genes for a given functional term that are identified in the expression data. The color represents the associated adjusted pvalue. 
	The X axis represents the gene ratio and the dot size the number of DEG genes associated to the functional term.\n\n"
)
pp <- dotplot(enrichments_ORA$REACT, showCategory=n_category)
plot(pp)

```




```{r go_main,  results='asis', echo = FALSE, eval = any(executed[["GO_BP"]],executed[["GO_MF"]],executed[["GO_CC"]])}
cat("## **Gene Ontology (GO) analysis**\n")
```

```{r go_bp_ora, results='asis', echo=FALSE, eval = all(executed[["GO_BP"]],exists("enrichments_ORA"))}

cat("### **[BP] Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"The plot shows the top functional terms in descendant order by gene ratio. This ratio is the proportion of the known genes for a given functional term that are identified in the expression data. The color represents the associated adjusted pvalue. 
	The X axis represents the gene ratio and the dot size the number of DEG genes associated to the functional term.\n\n"
)
pp <- dotplot(enrichments_ORA$GO_BP, showCategory=n_category)
plot(pp)

```

```{r go_mf_ora, results='asis', echo=FALSE, eval = all(executed[["GO_MF"]],exists("enrichments_ORA"))}

cat("### **[MF] Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"The plot shows the top functional terms in descendant order by gene ratio. This ratio is the proportion of the known genes for a given functional term that are identified in the expression data. The color represents the associated adjusted pvalue. 
	The X axis represents the gene ratio and the dot size the number of DEG genes associated to the functional term.\n\n"
)
pp <- dotplot(enrichments_ORA$GO_MF, showCategory=n_category)
plot(pp)

```

```{r go_cc_ora, results='asis', echo=FALSE, eval = all(executed[["GO_CC"]],exists("enrichments_ORA"))}

cat("### **[CC] Over Representation Analysis**\n",
	"The ORA method takes a group of significative DEGs (only DEGs, upregulated DEGs or downregulated DEGs) and performs a hypergeometric test for each term of the selected functional category.\n\n")

cat(
	"**Dotplot**\n\n", 
	"The plot shows the top functional terms in descendant order by gene ratio. This ratio is the proportion of the known genes for a given functional term that are identified in the expression data. The color represents the associated adjusted pvalue. 
	The X axis represents the gene ratio and the dot size the number of DEG genes associated to the functional term.\n\n"
)
pp <- dotplot(enrichments_ORA$GO_CC, showCategory=n_category)
plot(pp)

```