



### **Principal Component Analysis**
This is a PCA plot of the count values normalized following the default method and then they are scaled:

```{r , echo = FALSE, results = "asis", warning = TRUE, message = TRUE}
std_pca <- FactoMineR::PCA(pca_data, scale.unit=TRUE, graph = FALSE)                                                     
dim_to_keep <- get_PCA_dimensions(std_pca)

rownames(target) <- as.character(target$sample)
string_factors <- final_main_params$string_factors
numeric_factors <- final_main_params$numeric_factors

pca_data <- merge_factors(pca_data, target, string_factors)
pca_data <- merge_factors(pca_data, target, numeric_factors)

full_pca <- FactoMineR::PCA(pca_data,ncp = dim_to_keep, scale.unit=TRUE, graph = FALSE, quanti.sup = numeric_factors, quali.sup=string_factors)
``` 
#### **Representation of the samples in the two first dimension of PCA** 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'} 
FactoMineR::plot.PCA(full_pca, invisible = "quali" , title = "")
``` 

#### **Representation of the samples and the categories of qualitative valiables in the two first dimension of PCA** 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'} 

FactoMineR::plot.PCA(full_pca, title = "")
```

#### **Representation of the variable contribution to the PCA axis 1 and 2**

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = !is.null(numeric_factors)} 
factoextra::fviz_pca_var(full_pca, axes = c(1, 2),select.var = list(name=numeric_factors), col.var="steelblue", title="") +
		ggplot2::theme_minimal()

``` 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = (dim_to_keep > 3 & !is.null(numeric_factors)) } 
cat("#### **Representation of the variable contribution to the PCA axis 3 and 4**")

factoextra::fviz_pca_var(full_pca, axes = c(3, 4),select.var = list(name=numeric_factors), col.var="steelblue", title="") +
		ggplot2::theme_minimal()

``` 


```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = !is.null(numeric_factors)} 
cat("#### **Representation of the individuals and the variable contribution to the PCA axis 1 and 2**")
factoextra::fviz_pca_biplot(full_pca, repel = TRUE,select.var = list(name=numeric_factors), col.var="steelblue", title="") +
		ggplot2::theme_minimal()

```

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'}
cat(paste("#### **Hierarchical clustering of individuals using first", dim_to_keep, "significant PCA dimensions**",sep=' '))
res.hcpc <- FactoMineR::HCPC(full_pca, graph = FALSE)
plot(res.hcpc , choice="tree", title="")

```

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'}
cat(paste("#### **PCA representation of 1 and 2 axis with individuals coloured by its cluster membership. The first ", dim_to_keep, "significant PCA dimensions are used for HCPC**",sep=' '))
plot(res.hcpc , axes=c(1,2), choice="map", draw.tree= FALSE, title="")
```

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'}

dim_data <- FactoMineR::dimdesc(full_pca, axes=seq(1, dim_to_keep))


dim_data_simp <- dim_data[grepl("Dim",names(dim_data))]
test <- lapply(names(dim_data_simp), parse_dim_table, dim_data = dim_data_simp, tag = "####")

```
