



### **Principal Component Analysis**
This is a PCA plot of the count values normalized following the default method and then they are scaled:

#### **Inertia plot exploring variance explained by dimensions**

Graphical representation of PCA dimensions. The bars represent the percentage of total variance that summarize each dimension. 
The line measures the percentage of total variance accumulated in previous dimensions. The color distinguishes between significan or no significant dimensions. 
Only significant dimensions will be considered in the following plots.
```{r, echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', fig.width = 5, fig.height = 4 }
inertia <- as.data.frame(pca_data$eig)[,c(2,3)]
inertia$names <- factor(gsub("comp ", "PC", rownames(inertia)), levels= gsub("comp ", "PC", rownames(inertia)))
colnames(inertia) <- c("var", "cum_var", "names")
inertia$sig <- ifelse(rownames(inertia) %in% paste("comp", seq(1, dim_to_keep)), "significant", "no_significant")
ggplot2::ggplot(inertia) + ggplot2::geom_bar(ggplot2::aes(x = names, y = var, fill = sig), stat = "identity") + 
ggplot2::geom_line(ggplot2::aes(x = names, y = cum_var), stat = "identity", group = 1)+ 
ggplot2::labs(x = "", y = "Percentage of total variance")+ 
ggplot2::scale_y_continuous(sec.axis = ggplot2::sec_axis(~./100, name = "Cumulative percentage of variance", labels = scales::percent)) + 
ggplot2::theme(legend.position = "bottom", axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))

```


#### **Distribution of Eigenvectors**
The eigenvector contains the weights of each gene for the PC. Here are represented the distributions of the weights of each eigenvector.
The vertical lines represent the quantiles. 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', fig.width = 5, fig.height = 4 }

eig_dist <- pca_data$svd$V
colnames(eig_dist) <- colnames(pca_data$var$cor)
eig_dist <- reshape2::melt(eig_dist)

ggplot2::ggplot(eig_dist, ggplot2::aes(x = value, 
                                            y = Var2)) + 
ggridges::geom_density_ridges(jittered_points = TRUE, 
                              position = "raincloud", 
                              alpha = 0.7, 
                              scale = 0.9, 
                              quantile_lines = TRUE) + 
ggplot2::theme_classic()
```

#### **Comparison of significant dimensions significant dimensions**

This plot compare the position of samples and their distribution in the significant dimensions. 
The color differenciate between the control (red) and treat (blue) samples. 

```{r, echo = FALSE,warning =FALSE, message=FALSE, results = 'asis', fig.width = 8, fig.height = 8, eval = !is.null(target) }

dims <- as.data.frame(pca_data$ind$coord)
colnames(dims) <- gsub("Dim.", "PC", colnames(dims))
inertia$text <- paste(inertia$names, "\n(", round(inertia$var, 2),"%)", sep = "")
colnames(dims)[colnames(dims) %in% inertia$names] <- inertia$text[match(colnames(dims), inertia$names)]
dims$names <- rownames(dims)
rownames(dims) <- NULL
dims <- merge(dims, target[,c("sample","treat")], by.x = "names", by.y ="sample")

pca_scatter <- function(data, mapping,...){
	 p <- ggplot2::ggplot(data, mapping)  
	 p$mapping$alpha <- NULL
	 p$mapping$color <- p$mapping$fill
	p + ggplot2::geom_point() + 
	ggplot2::geom_vline(xintercept = 0,  linetype="dashed")+ 
	ggplot2::geom_hline(yintercept = 0,  linetype="dashed")
}

p <- GGally::ggpairs(dims, columns = seq(2, dim_to_keep +1),  
	mapping = ggplot2::aes(fill = treat, alpha = 0.5),
	lower = list(continuous = pca_scatter),
	upper = list(continuous = "blank"), 
	switch = "both") + 
	ggplot2::theme_bw() 

p[dim_to_keep, dim_to_keep] <- p[dim_to_keep, dim_to_keep] +ggplot2::coord_flip()
p
```

#### **Representation of the samples in the two first dimension of PCA** 
```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'} 
FactoMineR::plot.PCA(pca_data, invisible = "quali" , title = "")
``` 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = !is.null(target) } 
FactoMineR::plot.PCA(pca_data, invisible = "quali" , title = "", label = "none", habillage = "treat")
```

#### **Representation of the samples and the categories of qualitative valiables in the two first dimension of PCA** 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'} 

FactoMineR::plot.PCA(pca_data, title = "")
```


```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = !is.null(numeric_factors)} 
cat("#### **Representation of the variable contribution to the PCA axis 1 and 2**")

factoextra::fviz_pca_var(pca_data, axes = c(1, 2),select.var = list(name=numeric_factors), col.var="steelblue", title="") +
		ggplot2::theme_minimal()

``` 

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = (dim_to_keep > 3 & !is.null(numeric_factors)) } 
cat("#### **Representation of the variable contribution to the PCA axis 3 and 4**")

factoextra::fviz_pca_var(pca_data, axes = c(3, 4),select.var = list(name=numeric_factors), col.var="steelblue", title="") +
		ggplot2::theme_minimal()

``` 


```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', eval = !is.null(numeric_factors)} 
cat("#### **Representation of the individuals and the variable contribution to the PCA axis 1 and 2**")
factoextra::fviz_pca_biplot(pca_data, repel = TRUE,select.var = list(name=numeric_factors), col.var="steelblue", title="") +
		ggplot2::theme_minimal()

```

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'}
cat(paste("#### **Hierarchical clustering of individuals using first", dim_to_keep, "significant PCA dimensions**",sep=' '))
plot(res.hcpc , choice="tree", title="")

```

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'}
cat(paste("#### **PCA representation of 1 and 2 axis with individuals coloured by its cluster membership. The first ", dim_to_keep, "significant PCA dimensions are used for HCPC**",sep=' '))
plot(res.hcpc , axes=c(1,2), choice="map", draw.tree= FALSE, title="")
```


#### **Relationship between HCPC clusters and experiment design**
Fisher's exact test is computed between clusters and experimental treats. Fisher's exact test P values and FDR are showed. 
```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis'}

all_factor_clusters <- data.frame()
for (add_factor in string_factors) {
	clusters_ct <- ct_from_qual(res.hcpc$data.clust[,c("clust", add_factor)])
	clusters_ct$sub <- paste(add_factor,clusters_ct$sub, sep = ":")
	colnames(clusters_ct)[match(c("ref","sub"),colnames(clusters_ct))] <- c("Cluster","Category")
	clusters_ct$fisher.test.pval <- v.fisher.test(clusters_ct)
	clusters_ct$FDR <- p.adjust(clusters_ct$fisher.test.pval, method = "BH")
	all_factor_clusters <- rbind(all_factor_clusters, clusters_ct)
}

all_factor_clusters <- all_factor_clusters[all_factor_clusters$FDR <= 0.05,]

if (nrow(all_factor_clusters) > 0 ) {

	all_factor_clusters$FDR <- format(all_factor_clusters$FDR, scientific = TRUE, digits = 3)
	all_factor_clusters$fisher.test.pval <- format(all_factor_clusters$fisher.test.pval, scientific = TRUE, digits = 3)

	all_factor_clusters <- all_factor_clusters[,c("Cluster","Category","fisher.test.pval", "FDR")]


	DT::datatable(all_factor_clusters, filter = 'top', rownames = FALSE, 
                      extensions = c('Buttons','ColReorder'),
                      options = list(
                        colReorder = TRUE,
                        dom = 'lftBip',
                          buttons = c('copy', 'csv', 'excel')))

	# knitr::kable(all_factor_clusters, row.names = FALSE)
} else {
	cat("None of the clusters were significantly associated with any experimental group")

}

```

#### **Representation of correlation and P value of numeric factors and PCA dimensions**

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', fig.width = 5, fig.height = 5}
dim_data_quant <- dim_data_merged$quantitative
dim_data_quant <- dim_data_quant[dim_data_quant$factor %in% numeric_factors,]
if (nrow(dim_data_quant) > 0 ) {
	dim_data_quant$dimension <- gsub("Dim.", "PC", dim_data_quant$dimension)
	dim_data_quant$correlation <- round(dim_data_quant$correlation, digits = 2)
	dim_data_quant$significance <- ifelse(dim_data_quant$p.value < 0.001, "***",
					                ifelse(dim_data_quant$p.value < 0.01, "**",
				                    ifelse(dim_data_quant$p.value < 0.05, "*", "")))
	dim_data_quant$text_corr <- paste(as.character(dim_data_quant$correlation),as.character(dim_data_quant$significance), sep = " ")


	gg_heatmap(dim_data_quant, x_axis="dimension", y_axis="factor",fill = "correlation", 
		text_plot="text_corr", text_size = 4,
		col = c("#3b71ff", "#f1f1f1", "#ff3b3b"))

} else {
	cat("None of the factors were significantly associated with any dimension")
}
```

#### **Representation of R2 and P value of qualitative factors and PCA dimensions**

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', fig.width = 5, fig.height = 5}

dim_data_qual <- dim_data_merged$qualitative
if (nrow(dim_data_qual) >0 ) {
	dim_data_qual$dimension <- gsub("Dim.", "PC", dim_data_qual$dimension)
	dim_data_qual$R2 <- round(dim_data_qual$R2, digits = 3)
	dim_data_qual$significance <- ifelse(dim_data_qual$p.value < 0.001, "***",
					                ifelse(dim_data_qual$p.value < 0.01, "**",
				                    ifelse(dim_data_qual$p.value < 0.05, "*", "")))

	dim_data_qual$text_adjust <- paste(as.character(dim_data_qual$R2),as.character(dim_data_qual$significance), sep = " ")

	gg_heatmap(dim_data_qual, x_axis="dimension", y_axis="factor",fill = "R2", text_plot="text_adjust", text_size = 4,
		col = c("#3b71ff", "#f1f1f1", "#ff3b3b"))

} else {
	cat("None of the factors were significantly associated with any dimension")
}
```

#### **Representation of estimated coordinated from barycentre and P value of qualitative factors and PCA dimensions**

```{r , echo = FALSE, warning =FALSE, message=FALSE, results = 'asis', fig.width = 5, fig.height = 5}

dim_data_cat <- dim_data_merged$qual_category
if (nrow(dim_data_cat) >0 ) {
	dim_data_cat$dimension <- gsub("Dim.", "PC", dim_data_cat$dimension)

	dim_data_cat$significance <- ifelse(dim_data_cat$p.value < 0.001, "***",
					                ifelse(dim_data_cat$p.value < 0.01, "**",
				                    ifelse(dim_data_cat$p.value < 0.05, "*", "")))
	dim_data_cat$text_estimate <- paste(round(dim_data_cat$Estimate, digits = 4),dim_data_cat$significance, sep = " ")
	gg_heatmap(dim_data_cat, x_axis="dimension", y_axis="factor",fill = "Estimate", text_plot="text_estimate", text_size = 4,
		col = c("#3b71ff", "#f1f1f1", "#ff3b3b") )

} else {
	cat("None of the categories were significantly associated with any dimension")
}
```