---
author: "SysBioLab"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<style type='text/css'>
    body .main-container { 
        max-width: 80%;
    
    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>


# **CoRmiT: RNAseq - miRNAseq correlation report**

This report summarizes the results of ExpHunterSuite CoRmiT, comparing RNAseq and miRNAseq data and looking for putative miRNA-gene target interactions based on different strategies.

```{r config, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE}

cols <- c("Eg Em"= "#1F77B4", "Cg Cm"="#FF7F0E", "Eg Cm"="#2CA02C", "Hg Cm"="#D62728", "Eg Hm"="#9467BD", "Hg Em"="#8C564B", "Hg Hm"="#E377C2", "Cg Hm" ="#767676", "Cg Em" ="#000000" ) #, "#7F7F7F", "#BCBD22", "#17BECF")

```
## **General Overview - Quality Control**

This section describes the general statistics about coRmiT execution.


### **Executed strategies**

```{r executes_str, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE}
all_cor_dist_fil <- all_cor_dist[!all_cor_dist$strategy %in% c("DEGs_RNA_vs_miRNA_DEMs_opp", "DEGs_RNA_vs_miRNA_DEMs_sim") &
                                 !grepl("Eigengene_0" ,all_cor_dist$strategy),]
all_cor_dist_fil$strategy <- as.factor(all_cor_dist_fil$strategy)
all_cor_dist_fil$strategy_old <- all_cor_dist_fil$strategy 
levels(all_cor_dist_fil$strategy) <- set_strats_readable(levels(all_cor_dist_fil$strategy))

strat_n <- unique(all_cor_dist_fil[,c("strategy", "strategy_old")])

strat_n$strategy_old <- gsub("_", " ", strat_n$strategy_old)
colnames(strat_n) <- c("Strategy name", "Description")
knitr::kable(strat_n, row.names = FALSE)

cat(paste(paste(unique(cont_tables$corr_cutoff), collapse =", "), "correlation thresholds have been applied to each strategies."))

```


### **Correlation distributions**

Distributions of correlation values between miRNAs and target genes obtained using the different strategies.
Horizontal white lines within the distributions represent the 90 and 95 percentiles. 

```{r methods_comparison_violin_cor, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE}
all_cor_dist_fil <- all_cor_dist[!all_cor_dist$strategy %in% c("DEGs_RNA_vs_miRNA_DEMs_opp", "DEGs_RNA_vs_miRNA_DEMs_sim") &
                                 !grepl("Eigengene_0" ,all_cor_dist$strategy),]
all_cor_dist_fil$strategy <- as.factor(all_cor_dist_fil$strategy)
all_cor_dist_fil$strategy_old <- all_cor_dist_fil$strategy 
levels(all_cor_dist_fil$strategy) <- set_strats_readable(levels(all_cor_dist_fil$strategy))

pp <- ggplot2::ggplot(all_cor_dist_fil, ggplot2::aes(x = strategy, y = correlation, fill = strategy)) +
  ggplot2::geom_violin(col = "white",trim = FALSE, scale = "width",draw_quantiles = c(0.1, 0.05)) + #ggplot2::ylim(-1.000001, min + 0.00001) +
  ggplot2::geom_boxplot(width=0.05)+ ggplot2::ylim(-1, 1) +
  ggplot2::coord_flip() +
  ggplot2::theme(axis.text.y = ggplot2::element_blank(), axis.title.y = ggplot2::element_blank()) +
  ggplot2::labs(fill = "Strategy") + 
  ggplot2::scale_fill_manual(values = cols)

pp
```

### **Correlation P values distribution**

Distributions of correlation P values between miRNAs and target genes obtained using the different strategies.
The dashed line represents a threshold of 0.05 

```{r methods_comparison_violin_p, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE}

pp <- ggplot2::ggplot(all_cor_dist_fil, ggplot2::aes(x = strategy, y = pval, fill = strategy)) +
  ggplot2::geom_violin(trim = FALSE, scale = "width") + 
  ggplot2::geom_boxplot(width=0.05)+ ggplot2::ylim(-0.01, 1) +
  ggplot2::geom_hline(yintercept = 0.05, colour="grey", linetype = "dashed")+
  ggplot2::coord_flip() +
  ggplot2::theme(axis.text.y = ggplot2::element_blank(), axis.title.y = ggplot2::element_blank()) +
  ggplot2::labs(fill = "Strategy") + 
  ggplot2::scale_fill_manual(values = cols)
pp

```

### **Overal Odds Ratio**

Overall Odds Ratio was computed as an overview of strategies performance. 
The color indicate the strategies and shape and linetype represent the type of strategy. 
Y axis represent Overall Odds Ratio and X represent the correlation thresholds. 

```{r overall_OR, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10  }
cont_tables$strategy <- set_strats_readable(cont_tables$strategy)
cont_tables <- cont_tables[!grepl("DEG",cont_tables$strat) & !grepl("E0",cont_tables$strat),]

strat_names <- t(as.data.frame(strsplit(cont_tables$strategy, " ")))

cont_tables$RNA_strat <- strat_names[,1]
cont_tables$miRNA_strat <- strat_names[,2]


cont_tables_pred <- cont_tables[cont_tables$db_group == "multimir",]
ggplot2::ggplot(cont_tables_pred, ggplot2::aes(x=corr_cutoff, y=Odds_ratio,color = strategy)) +
            ggplot2::geom_point(ggplot2::aes( shape = RNA_strat),size = 4, stat="identity", alpha = 0.8) +
            ggplot2::geom_line(ggplot2::aes(linetype = miRNA_strat), size = 0.7, stat="identity", alpha = 0.8)+
            ggplot2::xlab("Pearson's R threshold") + ggplot2::ylab("Odds ratio") +
            ggplot2::theme_minimal()+
      ggplot2::theme(legend.position="bottom",
            legend.box = "vertical",
            axis.text = ggplot2::element_text(size = 17),
            axis.title = ggplot2::element_text(size = 20, face = "bold"),
            legend.text = ggplot2::element_text(size = 17),
            legend.title = ggplot2::element_text(size=17, face = "bold")) +
      ggplot2::guides(colour = ggplot2::guide_legend(nrow = 4))+
      ggplot2::scale_color_manual(name = "Strategy",
                                  values = cols)


```


## **Integrated pairs description**

This section describes the optimal pairs for each miRNA were selected through the Selecction-Integration.
(Further description in Cordoba-Caballero et al., 2024)

### **General overview of integrated pairs**

```{r overall_results_table, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.width = 4, fig.height = 4}
      overall_stats <- all_pairs[!is.na(all_pairs$normalized_counts_RNA_vs_miRNA_normalized_counts_correlation),]
      overall_stats$miRNA <- mirna_names[match(overall_stats$miRNAseq, mirna_names$ACCESSION), "NAME"]

      int_stats <- overall_stats[overall_stats$miRNA %in% unique(miRNA_cont_tables[miRNA_cont_tables$db_group == "multimir", "miRNA"]),]
      int_stats <- int_stats[int_stats$integrated_strat,]
      overall_summary <- data.frame("Input miRNA" = length(unique(overall_stats$miRNAseq)),
                                    "Input RNA" = length(unique(overall_stats$RNAseq)),
                                    "miRNA with targets" = length(unique(int_stats$miRNAseq)),
                                    "RNA targets" = length(unique(int_stats$RNAseq)),
                                    "Total integrated pairs" = nrow(int_stats),
                                    "Pairs in any DBs" = sum(int_stats$multimir),
                                    "Pairs in prediction DBs" = sum(int_stats$predicted),
                                    "Pairs in validation DBs" =sum(int_stats$validated)
                                    , check.names = FALSE)
      overall_summary <- as.data.frame(t(overall_summary))
      colnames(overall_summary) <- "Count"
knitr::kable(overall_summary)

```

### **Selected strategy for miRNAs**
Selection-Integration methods select, for each miRNA, the optimal strategy and correlation threshold based on Specific Odds Ratio.
This plot shows the strategy (color) and correlation threshold (black tags over the bars) for each miRNA. 
White numbers represent the number of pairs that were found in DBs for each miRNA. Y axis represent the Specific Odds Ratio.

```{r miRNA_best_strategy, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5}
   miRNA_cont_tables_mult <- miRNA_cont_tables[miRNA_cont_tables$db_group == "multimir",]
miRNA_cont_tables_mult$strategy <- set_strats_readable(miRNA_cont_tables_mult$strategy)
  best_strats_mult <- select_best_strategy(miRNA_cont_tables_mult)

  best_strats_mult$strat_corr<- paste(best_strats_mult$strategy , as.character(best_strats_mult$corr_cutoff), sep = " ")
  best_strats_mult$strat_pairs <- as.character(best_strats_mult$TP+ best_strats_mult$FP)

  ggplot2::ggplot(best_strats_mult, ggplot2::aes(x = miRNA, y = Odds_ratio, fill  = strategy)) + 
  ggplot2::geom_bar(stat = "identity", width = 0.8) + 
  ggplot2::geom_text(ggplot2::aes(label=as.character(corr_cutoff)), vjust=-0.3, size=3.5,  colour = "black") +
  ggplot2::geom_text(ggplot2::aes(label = TP), size=3.5, vjust = 1.5, colour = "white")+
  ggplot2::scale_fill_manual(values = cols) + 
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60,hjust=1,vjust=1, size = 18),
                 axis.text.y = ggplot2::element_text(size = 18), 
                 axis.title.y = ggplot2::element_text(size = 18, face = "bold"),
                 axis.title.x = ggplot2::element_text())


```


### **Best Strategy based on multimir pairs**

This table shows different statistics about optimal strategy for each miRNA.

```{r best_strat_mult, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE}

best_strats_to_print <- best_strats_mult[,c("miRNA","strategy","TP", "Odds_ratio", "corr_cutoff", "p.adjust")]
colnames(best_strats_to_print) <- c("miRNA","Strategy","Pairs in DBs", "Specific Odds Ratio", "Correlation cutoff", "Fisher's exact test FDR")
knitr::kable(best_strats_to_print)
```

### **Strategy summary based on multimir pairs**

This table summarizes the impact of different strategies in the integrated pairs.
miRNA_count is the number of miRNA for which the strategy was the optimal. 
median_OR represent the median of the Specific Odds Ratio distribution of all miRNA for which the strategy was the optimal.

```{r strat_summary, echo=FALSE, results = 'asis', warning = FALSE, message = FALSE}
library(dplyr) #remove
strat_sum <- best_strats_mult %>% group_by(strategy) %>% summarise(miRNA_count = length(miRNA), median_OR = median(Odds_ratio))
knitr::kable(strat_sum)
```
