
---
author: "José Córdoba Caballero"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
    	overflow: scroll;
  		max-height: 600px;
  	}

    .plot_real_size img{
    	max-width: none;
    	max-height: none;
    }

    embed {
   
  }   
</style>

```{r config, include = FALSE}
n_category <- 30
base_width <- 30


# Load necessary packages
require(ggplot2)
require(knitr)
require(plyr)
require(clusterProfiler)
require(DT)

# Prepare all HPO reports container
out <- NULL

# Check executed modules
all_posible <- c("GO_BP","GO_CC","GO_MF","KEGG","REACT")
executed <- as.list(all_posible %in% names(enrichments_ORA))
names(executed) <- all_posible

for (nomenc in names(enrichments_ORA)) {
	if (!length(get_categories(enrichments_ORA[[nomenc]])) > 0){
		executed[[nomenc]] <- FALSE
	}
}

col <- c("#89C5DA", "#DA5724", "#74D944", "#CE50CA", "#3F4921", "#C0717C", "#CBD588", "#5F7FC7", 
         "#673770", "#D3D93E", "#38333E", "#508578", "#D7C1B1", "#689030", "#AD6F3B", "#CD9BCD", 
         "#D14285", "#6DDE88", "#652926", "#7FDCC0", "#C84248", "#8569D5", "#5E738F", "#D1A33D", 
         "#8A7C64", "#599861")

```

# miRNA target genes functional report

Functional results for the targets of each miRNA, combined. Target genes for each miRNA were subjected to over respresentation analysis (ORA). 
The ORA method uses Fisher exact test to find enrichment for functional categories within a list of genes.

```{r kegg_main,  results='asis', echo = FALSE, eval = executed[["KEGG"]]}
cat("## **KEGG analysis**\n")
```
```{r kegg_ora, results='asis', echo=FALSE, eval = executed[["KEGG"]], message = FALSE, warning = FALSE}



plot_enrResult_DT(enrichments_ORA$KEGG)


cat(
	"**Dotplot**\n\n", 
	"Functional categories enriched among the targets for each miRNA (x-axis). 
	 The total number of target genes found within the functional categories are indicated in brackets below the miRNA name.
	 Size of dot represents the gene ratio, defined as the proportion of significant genes that are found in the functional category.
	 \n\n"
)

# cat(length(get_categories(enrichments_ORA$KEGG)))
pp <- enrichplot::dotplot(enrichments_ORA$KEGG, showCategory=n_category) 
pp <- set_standard_size(pp)
invisible(plot_in_div(pp, calc_height(enrichments_ORA$KEGG), calc_width(enrichments_ORA$KEGG)))



cat('\n\n**Enrich Map plot**\n\n', 
	'Nodes represent functional categories, connected if they share genes, with thicker edges indicating a greater number of shared genes. 
	The size of the node represents the number of genes belonging to that category. 
	Each node is a pie chart, showing the proportion of genes correlated with each miRNA.\n\n'
)


pp <- enrichplot::emapplot(enrichments_ORA$KEGG, showCategory=n_category,pie="count", pie_scale=1.5, layout="kk") + ggplot2::scale_fill_manual(values = col)

invisible(plot_in_div(pp, fig_height = 6, fig_width = 6))



```



```{r reac_main,  results='asis', echo = FALSE, eval = executed[["REACT"]]}
cat("## **Reactome analysis**\n")
```
```{r reac_ora, results='asis', echo=FALSE, eval = executed[["REACT"]], warning = FALSE, message = FALSE}
# save.image(file = file.path(debug_folder, "debug.RData"))

# cat("### **Over Representation Analysis**\n",
# 	"The ORA method takes a group of significant genes and performs a Fisher's exact test for each term of the selected functional category.\n\n")

plot_enrResult_DT(enrichments_ORA$REACT)


cat(
	"**Dotplot**\n\n", 
	"Functional categories enriched among the targets for each miRNA (x-axis). 
	 The total number of target genes found within the functional categories are indicated in brackets below the miRNA name.
	 Size of dot represents the gene ratio, defined as the proportion of significant genes that are found in the functional category.
	 \n\n"
)
# cat(length(get_categories(enrichments_ORA$REACT)))

pp <- enrichplot::dotplot(enrichments_ORA$REACT, showCategory=n_category)  
pp <- set_standard_size(pp)
invisible(plot_in_div(pp, calc_height(enrichments_ORA$REACT), calc_width(enrichments_ORA$REACT)))


# cat(
# 	"**Heatmap**\n\n", 
# 	"WRITE THIS TEXT >>>>.\n\n"
# )

# pp <- clusters_heatplot(enrichments_ORA$REACT@compareClusterResult)  
# pp <- set_standard_size(pp)
# plot_in_div(pp, calc_height(enrichments_ORA$REACT),calc_width(enrichments_ORA$REACT))

cat('\n\n**Enrich Map plot**\n\n', 
	'Nodes represent functional categories, connected if they share genes, with thicker edges indicating a greater number of shared genes. 
	The size of the node represents the number of genes belonging to that category. 
	Each node is a pie chart, showing the proportion of genes correlated with each miRNA.\n\n'
)
pp <- enrichplot::emapplot(enrichments_ORA$REACT, showCategory=n_category, pie="count", pie_scale=1.5, layout="kk")+ ggplot2::scale_fill_manual(values = col)
invisible(plot_in_div(pp, fig_height = 6, fig_width = 6))


```




```{r go_main,  results='asis', echo = FALSE, eval = any(executed[["GO_BP"]], executed[["GO_MF"]], executed[["GO_CC"]]), warning = FALSE, message = FALSE}
cat("## **Gene Ontology (GO) analysis**\n")
```

```{r go_bp_ora, results='asis', echo=FALSE, eval = executed[["GO_BP"]], warning = FALSE, message = FALSE}

 cat("### **[BP] Over Representation Analysis**\n")
# ,
# 	"The ORA method takes a group of significant genes and performs a Fisher's exact test for each term of the selected functional category.\n\n")

plot_enrResult_DT(enrichments_ORA$GO_BP)


cat(
	"**Dotplot**\n\n", 
	"Functional categories enriched among the targets for each miRNA (x-axis). 
	 The total number of target genes found within the functional categories are indicated in brackets below the miRNA name.
	 Size of dot represents the gene ratio, defined as the proportion of significant genes that are found in the functional category.
	 \n\n"
)
# cat(length(unique(get_categories(enrichments_ORA$GO_BP, showCategory = n_category))))

pp <- enrichplot::dotplot(enrichments_ORA$GO_BP, showCategory=n_category)  
pp <- set_standard_size(pp)
invisible(plot_in_div(pp, calc_height(enrichments_ORA$GO_BP, showCategory=n_category), calc_width(enrichments_ORA$GO_BP)))


# cat(
# 	"**Heatmap**\n\n", 
# 	"WRITE THIS TEXT >>>>.\n\n"
# )

# pp <- clusters_heatplot(enrichments_ORA$REACT@compareClusterResult) 
# pp <- set_standard_size(pp)
# plot_in_div(pp, calc_height(enrichments_ORA$GO_BP),calc_width(enrichments_ORA$GO_BP))

cat('\n\n**Enrich Map plot**\n\n', 
	'Nodes represent functional categories, connected if they share genes, with thicker edges indicating a greater number of shared genes. 
	The size of the node represents the number of genes belonging to that category. 
	Each node is a pie chart, showing the proportion of genes correlated with each miRNA.\n\n'
)
pp <- enrichplot::emapplot(enrichments_ORA$GO_BP, showCategory=n_category, pie="count", pie_scale=1.5, layout="kk")+ ggplot2::scale_fill_manual(values = col)
invisible(plot_in_div(pp, fig_height = 6, fig_width = 6))


```

```{r go_mf_ora, results='asis', echo=FALSE, eval = executed[["GO_MF"]], warning = FALSE, message = FALSE}

cat("### **[MF] Over Representation Analysis**")
# \n",
	# "The ORA method takes a group of significant genes and performs a Fisher's exact test for each term of the selected functional category.\n\n
	# ")

plot_enrResult_DT(enrichments_ORA$GO_MF)


cat(
	"**Dotplot**\n\n", 
	"Functional categories enriched among the targets for each miRNA (x-axis). 
	 The total number of target genes found within the functional categories are indicated in brackets below the miRNA name.
	 Size of dot represents the gene ratio, defined as the proportion of significant genes that are found in the functional category.
	 \n\n"
)
pp <- enrichplot::dotplot(enrichments_ORA$GO_MF, showCategory=n_category)  
pp <- set_standard_size(pp)
invisible(plot_in_div(pp, calc_height(enrichments_ORA$GO_MF), calc_width(enrichments_ORA$GO_MF)))

# cat(
# 	"**Heatmap**\n\n", 
# 	"WRITE THIS TEXT >>>>.\n\n"
# )

# pp <- clusters_heatplot(enrichments_ORA$GO_MF@compareClusterResult) 
# pp <- set_standard_size(pp)
# plot_in_div(pp, calc_height(enrichments_ORA$GO_MF), calc_width(enrichments_ORA$GO_MF))

cat('\n\n**Enrich Map plot**\n\n', 
	'Nodes represent functional categories, connected if they share genes, with thicker edges indicating a greater number of shared genes. 
	The size of the node represents the number of genes belonging to that category. 
	Each node is a pie chart, showing the proportion of genes correlated with each miRNA.\n\n'
)
pp <- enrichplot::emapplot(enrichments_ORA$GO_MF, showCategory=n_category, pie="count", pie_scale=1.5, layout="kk")+ ggplot2::scale_fill_manual(values = col)
invisible(plot_in_div(pp, fig_height = 6, fig_width = 6))
# cat(
# 	"**CNetplot**\n\n", 
# 	"WRITE THIS TEXT >>>>.\n\n"
# )
# pp <- cnetplot(enrichments_ORA$GO_MF, showCategory = n_category)
# plot_in_div(pp, calc_height(enrichments_ORA$GO_MF),calc_width(enrichments_ORA$GO_MF))

```

```{r go_cc_ora, results='asis', echo=FALSE, eval = executed[["GO_CC"]], warning = FALSE, message = FALSE}

cat("### **[CC] Over Representation Analysis**\n")
# ,
# 	"The ORA method takes a group of significant genes and performs a Fisher's exact test for each term of the selected functional category.\n\n")

plot_enrResult_DT(enrichments_ORA$GO_CC)


cat(
	"**Dotplot**\n\n", 
	"Functional categories enriched among the targets for each miRNA (x-axis). 
	 The total number of target genes found within the functional categories are indicated in brackets below the miRNA name.
	 Size of dot represents the gene ratio, defined as the proportion of significant genes that are found in the functional category.
	 \n\n"
)

pp <- enrichplot::dotplot(enrichments_ORA$GO_CC, showCategory=n_category)  
pp <- set_standard_size(pp)
invisible(plot_in_div(pp , calc_height(enrichments_ORA$GO_CC) ,calc_width(enrichments_ORA$GO_CC)))


# cat(
# 	"**Heatmap**\n\n", 
# 	"WRITE THIS TEXT >>>>.\n\n"
# )

# pp <- clusters_heatplot(enrichments_ORA$GO_CC@compareClusterResult) 
# pp <- set_standard_size(pp)
# plot_in_div(pp, calc_height(enrichments_ORA$GO_CC),calc_width(enrichments_ORA$GO_CC))


cat('\n\n**Enrich Map plot**\n\n', 
	'Nodes represent functional categories, connected if they share genes, with thicker edges indicating a greater number of shared genes. 
	The size of the node represents the number of genes belonging to that category. 
	Each node is a pie chart, showing the proportion of genes correlated with each miRNA.\n\n'
)
pp <- enrichplot::emapplot(enrichments_ORA$GO_CC, showCategory=n_category,pie="count", pie_scale=1.5, layout="kk")+ ggplot2::scale_fill_manual(values = col)
invisible(plot_in_div(pp, fig_height = 6, fig_width = 6))

```




```{r create_out_custom, echo = FALSE, warning = FALSE, message = FALSE}
out_custom <- ""
```

```{r custom_create, echo = FALSE, eval = exists("custom_targets_ORA"), warning = FALSE, message = FALSE}
out_custom <- NULL
invisible(lapply(seq_along(custom_targets_ORA),function(i){
	# Take results
	res <- custom_targets_ORA[[i]]
	cname <- names(custom_targets_ORA)[i]
	# Check and generate info
	if(is.null(res)){
		header <- "## **{{cname}}** \n\nThis CUSTOM study has been executed but **has not returned any result**\n"
		body <- ""
	}else{
		header <- ""

		body <- "res <- custom_targets_ORA[[{{i}}]]
				cname <- names(custom_targets_ORA)[{{i}}]
				cat('### **{{cname}} -  Over Representation Analysis**\n')
				# ,
				# 'The ORA method takes a group of significant genes and performs a Fisher's exact test for each term of the selected functional category.\n\n')
				
				plot_enrResult_DT(res)

				cat(
	              '**Dotplot**\n\n', 
	              'Functional categories enriched among the targets for each miRNA (x-axis). 
	               The total number of target genes found within the functional categories are indicated in brackets below the miRNA name.
	               Size of dot represents the gene ratio, defined as the proportion of significant genes that are found in the functional category.
	               \n\n')
				pp <- enrichplot::dotplot(res, showCategory=n_category)   
				pp <- set_standard_size(pp)
				invisible(plot_in_div( pp, calc_height(res),calc_width(res)))

				# cat(
				# 	'**Heatmap**\n\n', 
				# 	'WRITE THIS TEXT >>>>.\n\n'
				# )

				# pp <- clusters_heatplot(res@compareClusterResult) 
				# pp <- set_standard_size(pp)
				# plot_in_div(pp, calc_height(res),calc_width(res))

				cat('\n\n**Enrich Map plot**\n\n', 
				    'Nodes represent functional categories, connected if they share genes, with thicker edges indicating a greater number of shared genes. 
				    The size of the node represents the number of genes belonging to that category. 
				    Each node is a pie chart, showing the proportion of genes correlated with each miRNA.\n\n'
                   )
				pp <- enrichplot::emapplot(res, showCategory=n_category,pie='count', pie_scale=1.5, layout='kk')+ ggplot2::scale_fill_manual(values = col)
				invisible(plot_in_div(pp, fig_height = 6, fig_width = 6))

		"

	}
				# cat(
				# 	'**CNetplot**\n\n', 
				# 	'WRITE THIS TEXT >>>>.\n\n'
				# )

				# pp <- cnetplot(res, showCategory = n_category)
				# plot_in_div(pp, calc_height(res), calc_width(res))
	out_custom <<- c(out_custom,paste(knit_expand(text = paste(header,
										 					chunks(body, options = "echo = FALSE,results='asis'"),
										 					"\n",sep = "\n")),
													sep = "\n"))
}))

```

`r paste(knit(text = paste(out_custom,collapse = "\n")),collapse = "\n")`
